% DOCUMENT CLASS
    % Change "letterpaper" to "a4" if you use a4 paper size
    \documentclass[a4,12pt]{article}

    \usepackage{titlesec} % Allows customization of titles
    \usepackage{authblk} % For multiple authors
    \usepackage{amsmath}
    \usepackage[utf8]{inputenc}
	\usepackage{setspace} % See \doublespacing command at the top of content.tex
    \usepackage{lineno} 	% See \linenumbers at the top of content.tex
    \usepackage{booktabs}
    \usepackage[skip=2.5\baselineskip]{caption} % to give more space between figs and captions
    \usepackage{listings} % allows me to insert code 

% GRAPHICS
    \usepackage{graphicx} % More advanced figure inclusion
    \usepackage{float} % For specifying table/figure locations, i.e. [ht!]
    \usepackage[table,xcdraw]{xcolor}

\title{Estimating interaction networks for diverse, single-trophic communities}


\author[1]{Malyon D. Bimler}
\author[2]{Daniel B. Stouffer}
\author[4]{Margaret M. Mayfield}

\affil[1]{First affiliation address, with corresponding author email. Email: malyonbimler@gmail.com}
\affil[2]{Second affiliation address}
\affil[3]{Third affiliation address}

%\setcounter{page}{54}

\begin{document}
\maketitle  
\newpage
% \linenumbers

\tableofcontents

\section{Abstract}
    
    \begin{enumerate}
    \item Understanding ecological communities requires an understanding of how the different species within it relate to each other. Those relationships are difficult to quantify in single trophic systems such as plant communities because they cannot be directly observed as in food webs or other interaction networks, and must instead be inferred by other means. Current methods are inadequate for natural complex communities because they tend to rely on co-occurrence patterns (inaccurate) or intensive experimental designs (time-consuming, especially for many species). 
    \item We describe a general framework which allows us to estimate all pair-wise interactions in complex plant communities from empirical data and population dynamics models. This framework requires a multi-tiered approach to resolve all interactions. We first apply individual fitness models to each species in order to estimate interactions between species commonly observed to co-occur. We then use the resulting interactions to approximate interactions which were not observed using a different set of assumptions. 

    %Interactions between species which rarely co-occurred are then categorised as forbidden (true 0) or unrealised. Forbidden interactions are declared on the basis of spatial, phenological or physiological mismatches. Unrealised interactions are approximated using a response-effect model.
    \item This approach can be modelled using a Bayesian statistical framework which allows us to estimate interactions coefficients despite high model complexity, as well as quantify the uncertainty around the resulting community matrix. We discuss how the flexibility afforded by the Bayesian framework may also allow us to improve interaction estimates through the inclusion of environmental, phylogenetic and funtional trait data. 
    \item We suggest this approach be used for....
    \end{enumerate}


\section{Introduction}
    
    1. Networks are important tools for understanding ecosystems: functioning, stability, diversity + roles of species. Non-trophic interactions however are often omitted from networks! 


    2. We need networks for plants but unlie common 'network' ecosystems, we can't observe interactions -> they have to be deduced.
    
    3. A common way to do this is with species association networks because they require 'simple' data, can include lots of species, and there's lots of published methods out there (papers and packages of varying complexity). Unfortunately, cooc networks don't capture interactions (even when they're super complicated?!)

    4. Another way is to estimate from growth data. This is the approach plant people take, using population dynamic models. This is often done a low diversity scales (few species) because we need a lot of replication! 
    You can use observation data but still need complex models for many interactions! Current models only estimate alphas between a few species and keep them competitive. 


    5. We describe a modelling framework + implementation which ....



    Begin with the network introduction.

    There is a growing demand for plant networks because they're 1) useful to understand ecosys functioning and 2) plants are important systems to know more about. Multiple species.    

    Building plant networks is difficult, and a major challenge to understand how plant networks influence biodiversity is characterising interactions as they can't be directly observed. A popular way around this is to build cooccurrence networks. Though cooc networks may be useful for understanding association patterns, they are not proxies for interaction networks. 'Real' interactions can be measured from growth rate / fecundity / growth data. That can be complicated when there's a lot of species involved. 
    We propose a model framework that makes this easier.
 
  
    Non trophic interactions are usually neglected in ecological networks or lumped into compartments representing other primary producers of basal resources (Baiser et al., 2013; van der Zee et al., 2016; Borst et al., 2018 - in Ellison 2019).   

    Species interaction networks are fundamentally different to co-occurrence networks as they reflect per-capita effects on species' growth rates, rather than spatial association patterns. 
    Co-occurrence networks however, benefit from being easy to implement and can naturally handle a large number of species. There are in fact many  packages available in R to calculate these networks, with methods ranging from simple (cooccur package) to extremely complex (e.g. D Harris). 
    There are few however, published plant population dynamic models which are explicitely developped to include many species.

    \begin{itemize}
        \item Kokkoris2002 =  Competition / species interactions can contribute to diversity (read more)
        \item Levine2017 - beyond pairwise mechanisms of species coexistence in complex communities (read for intro)
        \item  Montoya2006a = Ecological networks are complex (interactions too) but useful for ecological mechanisms and understanding stability. [refhole?]
        \item Kefi2015 = 'non-random patterning of non-trophic interactions suggests a path forward for developing a more comprehensive ecological network theory to rpedict the functions and resilience of ecological communities'
    \end{itemize}

    \paragraph{}
    In particular, networks for annual plant communities have been requested, in part because of how much coexistence work is done on these systems. However, building networks for plant communities is challenging: they don't interact visibly, so we need to deduce interaction strengths from growing them at different densities and in different combinations of species. Even for a species-poor community grown in a greenhouse, this is very consuming in time, money and hours. Alternatively, we can estimate interactions from field observations which record fitness e.g. seed production (refs to Godoy, Wainwright, and others who have used this method). This has the advantage of allowing us to sample very diverse communities in 'natural' conditions. However, with the problem of adding many species comes the statistical/computing difficulty of estimating this many interactions.
    \begin{itemize}
        \item Losapio2019= methods and results of plant-plant networks [refhole]
        \item Godoy2014b = field parameterised models of competitor dynamics with pairs of 18 annual plant species
    \end{itemize}


    
    \paragraph{}
    We propose a general framework to estimate interactions between plants (or other single-trophic systems) in natural and complex communities. We allow for facilitative and competitive interactions both between and within species. 
    This framework merges multiple approaches (ifm, rem) and is implemented with Bayesian stats which allows us to estimate interactions between many species. 
    We suggest avenues for applications that make use of the rich information provided by interaction networks e.g. identifying key-stone species, exploring species strategies (motifs?), looking at how invasive species affect the rest of the network, identifying species at risk of population explosion (or extinction), etc...

    % Because of how much work is required to infer interaction strengths, some people have turned to cooccurrence networks as an alternative. This means using observational data (who is abundant where) and correlation/covariance/probabilistic methods to derive positive or negative associations between species, which is argued to be a proxy for the effect of one species on another (especially if environment is taken into account?). This approach is much quicker and cheaper, and is often used to infer species interactions in species distribution models for examples (?). However, recent works suggests that co-occurrence does not acurately reflect interactions, so their usefulness in understanding coexistence between species may be limited. 

    % \begin{itemize}
    %     \item Thurman2019 = 'co-occurrence methods are generally inaccurate when estimating trophic interactions'
    %     \item Zhu2019 = co-occurrence inadequate vs DNA barcodes on gut contents (plant-herbivore)
    %     \item Sander2017 = presence-absence data doesn't allow models to consistently identify species interactions in trophic and non-trophic networks
    % \end{itemize}

    % Co-occurrence networks also suffer from not being able to measure the effect (or rather association) of a species with itself. Yet these intraspecifc interactions are key to maintaining negative density-dependence, which is a vital component of coexistence theory. It would be nice if a reference exists which also says that co-occurrence methods underestimate facilitation, which is increasingly being recognised as an important force in communities which we have yet to integrate into theoretical frameworks of coexistence (another challenge!).  
    % \citep{Verdu2010} facilitation turns to competition between plants over time. Examines the phylogenetic structure of the network. Complexity of ecological interactions and complex network approaches - examine methods?
    
    
\section{Methods}
    
    This framework can be applied to any dataset of interacting species which meets the following criteria: 
    \begin{itemize}
        \item observations of focal individuals record a proxy for lifetime reproductive success (e.g. seed production, stem diameter growth, above-ground biomass)
        \item these observations also record the identity and abundance of neighbours within the interaction neighbourhood of each focal individual
        \item observations are replicated across several individuals of each focal species with varying neighbourhoods
    \end{itemize}
    In addition to these requirements, any experimental design or data which may reduce confounding effects between environment and competition will provide more accurate estimates of interaction strengths (e.g. thinning certain plots, recording environmental data known to affect reproductive success). 
    
    
    This framework also depends on an appropriate model of population dynamics for the system in question. The population dynamics model may require species-specific measures of certain key demographic rates (e.g. mortality, seedling survival). These rates are necessary in order to scale interaction coefficients such that they are comparable between species. 
    
    
    \subsection{IFM}
        
        We begin by implementing an individual fitness model to each focal species $i$ which regresses the identity and abundance of neighbours $j$ ($j = 1, 2, 3, ...$) against the measured proxy for lifetime reproductive success $F_{i}$:
        
        \begin{equation}
        F_{i} = \beta_{i0} - \sum_{i}^{j} \beta_{ij} N_{j}
        \label{ifm}
        \end{equation}
        
        The intercept $\beta_{i0}$ represents intrinsic fitness, a species' fitness in the absence of interactions with neighbours. $N_{j}$ are the abundances of neighbours recorded for each observation, and the $\beta_{ij}$ represent the species-specific effect of each neighbour $j$ on $i$. Note that neighbours can include conspecifics, in which case intraspecific interactions are denoted as $\beta_{ii}$.
              
    \subsection{Filling in the gaps}
        
        In any given site or year, a focal species may only be observed to interact with a subset of potential interaction partners, which means the IFM above will not be able to estimate all potential interactions ($\beta$) between species. This is especially true for rare species. In order to estimate the interactions missing from the IFM, we must separate those interaction which did not occur due to chance alone (\textit{unrealised links}) from those which cannot occur due to mismatches between species (\textit{forbidden links}). 
        
        % \subsubsection{Forbidden links}
        
        % \textit{Forbidden links} are those where two species cannot interact, because they cannot co-occur or are physiologically mismatched. An example from the food web literature would be a bird which cannot eat fruit which are too big for its beak. In plants, forbidden links can occur when species are spatially or temporally mismatched, due to different environmental requirements or varying phenologies. Forbidden links may also occur between species which have vastly different resource requirements such that the presence of one species does not affect the other, though in plants these require a great detail of physiological knowledge. In this paper, we limit ourselves to estimating forbidden links from spatial mismatches. \\
        
        % \textbf{Note: I dropped the section above as very very few interactions were 'forbidden' but I can bring it back?}

    \subsubsection{Unrealised links}
        
        Because sampling a community is not an exhaustive process, interactions between certain species may not have been observed even though the species in question are capable of interacting. These \textit{unrealised} interactions can be estimated by using an alternative model with a different set of assumptions to the IFMs. This model is described as the response-effect model (REM) by Godoy, Kraft and Levine (2014) and assumes that each species has the same effect on all neighbours regardless of their identity, as well as the same response to competition regardless of competitor identity. 
        
        \begin{equation}
        F_{i} = \beta_{i0} - \sum_{i}^{j} r_{i} e_{j} N_{j}
        \label{rem1}
        \end{equation}
        
        Pairwise interactions which are missing from Eq. 1 can be approximated by Eq. 2 by multiplying the relevant $r_{i}$ and $e_{j}$ such that $\beta_{ij} = r_{i} e_{j}$. In order to allow both the IFM and REM interaction estimates to contribute to the likelihood, we first used the IFM to quantify observed interactions and then used those to estimate species-specific $r$ and $e$ parameters such that: 
    
        \begin{equation}
        r_i e_j \sim logistic \left ( \alpha_{ij}, \sigma \right )
        \label{unrealised}
        \end{equation}
    
        where $\sigma$ is a community-level scale parameter for the logistic distribution. 
        
    \subsection{Scaling the interactions}
        
        After applying the IFMs, identifying forbidden links and estimating the remaining \textit{unrealised} interactions, the interactions effects returned by Eq. 1 and 2 must be scaled with appropriate demographic parameters determined by the system-specific model of population dynamics. This transformation puts interactions on the same scale, returning per-capita effects which are directly comparable between species. 
        
        In order to determine the appropriate scaling, the population dynamics model must first be transformed into a form equivalent to a Lotka-Volterra competition model. \textit{Figure out how to describe this in a general way, mention that the case study gives an explicit example.}
        
    \subsection{Model fitting}
        
        The IFMs (Eq. 1) and the REM (Eq. 2) can be implemented as generalised linear models in STAN, a Bayesian statistical language where coefficient values will be estimated by MCMC sampling. The advantage of this approach is two-fold: the model can converge and coefficients can be estimated despite high model complexity and a large number of parameters, and in case the data is insufficient we can get better estimates by using data from past experiments to constrain parameter priors. Readers familiar with STAN will note that it returns each parameter as a series of samples drawn from it's estimated distribution. This is important because ...

        We recommend that you group species that are too rare to make good estimates from - species which only have a handful of interactions. (Unless that goes to the case study section)
    
        \textit{Alternative paragraph to explain STAN ...}
        Stan is a probabilistic programming language used for Bayesian statistical inference which allows us to fit complex models even when the data is limited. Parameters are estimated as distributions which maximise the likelihood, and are conditioned by the data and priors which describe the distribution of plausible values which these parameters may take. The resulting parameter estimates are termed posterior distributions, and samples from the posterior are drawn for analysis.
        
        Whereas the IFMs are applied to each focal species, the response-effect model can be applied to to the dataset as a whole, with a different intercept ($\beta_{i0}$) for each focal species. \textit{Discuss how to verify that the rem will give good estimates: comparing model fit and estimates of $\beta_{i0}$ ...}

        The file used to specify and set the model in STAN is available in S.I. XX. 
    
    \subsection{Case study}

        We applied this framework to annual wildflower community dataset from Western Australia. This system is a diverse and well-studied community of annual plants which germinate, grow, set seed and die within approximately 4 months every year. Individual fecundity data were collected in 2016, when 100 50 x 50 cm plots established in the understory of West Perenjori Reserve (29$^o$28'01.3"S 116$^o$12'21.6"E) were monitered over the length of the full field season, from July to October. The resulting dataset contains from 29 to over 1000 counts of individual plant seed production from 22 different focal species (with a median of 108 observations per species), in addition to the identity and abundances of all neighbouring individuals within the interaction neighbourhood of the focal plant. Interaction neighbourhoods varied in radius from 3 to 5 cm depending on the size of the focal species. Neighbouring species which were recorded less than 10 times overall were grouped into a 'rare' category. Half of all plots were thinned (a quarter to 60\% diversity and a quarter to 30\%) to mitigate possible confounding effects between plot location and plant density, and did not target any particular species.\\

        Species demographic rates (seed and germination) for 16 of our focal species were estimated from a database of field experiments carried out between 2016 and 2019 where seedbags were placed in the field to estimate germination rates, and ungerminated seeds were evaluated in the lab for survivability. The remaining species were assigned mean demographic rates from these experiments. \\

        We applied the model using R and STAN and ran it with 4 chains and 5000 iterations per chain, discarding the first 1000. Models were checked for convergence and traceplots were visually inspected to verify good chain behaviour and mixing. Model parameters were sampled 1000 times from the 80\% posterior confidence intervals to construct our interaction estimates. We then applied bootstrap sampling from each resulting interaction strength distribution to create 1000 samples of the community interaction network.


\section{Results}


    The model framework we present here quantifies pair-wise interaction strengths between species from diverse single-trophic community data. Several aspects of our model and its implementation allow us to better capture complex features of plant communities compared to co-occurrence networks. Like co-occurrence networks, our framework is flexible to the inclusion of many species. Unlike co-occurrence networks, however, interactions in our model are estimated from species effects on each other's growth rates.  This allows us to capture how interactions may directly affect species abundances, rather than spatial association patterns. Two features make this possible: the response-effect model to estimate unobserved interactions, and a Bayesian implementation to deal with many parameters. The response-effect model allows us to deal with a small number of unobserved interactions by relaxing assumptions for those cases and estimating more general 'effect' and 'response' parameters from the pair-wise interactions that are observed. The Bayesian implementation means that parameters are estimated using MCMC algorithms, which can estimate more parameters than with more commonly used frequentist approaches (add REFs – find in Masters??). This approach also returns parameter estimates as posterior distributions rather than simple mean and standard deviations. By having access to the full distribution of likely values for every interaction, we can draw samples of likely networks from these distributions and thus incorporate some measure of variation and uncertainty around interaction values pretty easily.  \\


    Another way in which our method breaks from traditional plant population dynamic models is by allowing for facilitation. Associational networks and other approaches to interaction-based networks allow for competition alone (That’s not true, so qualify that statement – may talk a bit more about pop dyn approaches, and then also association?). Facilitation is well-known to be very important to community dynamics but is not explicitly measured or recognised by these approaches. Thus, our method allows us to investigate the effects of competition and facilitation at the same time, and across many species.   \\

     Our methods make it simpler for empiricists to estimate diverse interaction networks by providing an alternative to co-occurrence methods. Overall, our framework paints a more realistic picture of plant communities and their interactions: diversity is included, multiple interaction types can occur and unobserved interactions are not simply assigned to '0'. In turn, this allows empiricists to access network tools to better understand the plant communities and ecosystems they study, as well as non-trophic communities in general. \\



    % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    Of the 484 focal x focal interactions, 85\% were estimated using the IFM and 15\% using the REM. Including non-focal neighbours, the number of interactions to be estimated was 1144 and 60\% were estimated by the IFM

    Across all focal neighbour interaction, 65\% were competitive.

    % We built an interactio nmatrix for .... whole comm only. We estiamted so many interactions with the IFM and so many with the REM. So many interactions were competitive, whereas so many were facilitative. We estimated so many intraspecific interactions. Species node distribution followed an xx distribution. 

    % Suc hand such species are likely candidates for keystone species. Whearas x or y are connector species. Invasive species Arca and xx were not well embedded in the network, indicating that .... 

    % Our network differs remarquebly from a species association network, which would lead us to assume that x species is actually .. . Furthermore .... 


\section{Discussion}
    
    These two next paragraphs can be deleted or merged with the ‘results’ section above especially once I’ve added the extra results. 

 
    
    The model framework presented here allows the estimation of species-rich interaction matrices from plant community data. Our paper makes it easier for empiricists to characterise species interactions in their systems, as usually they need to come up with complex models to resolve all interactions. We provide a model for annual plant systems and a method which can be extended to any horizontal community for which there is a model of population dynamics - you will just need to adapt the model and scaling of interactions. \\

    The interaction matrices this model estimates are fundamentally different to association networks, which are a common alternative to estimating interactions in species-rich communities. Our estimates are direct per-capita effects of one species on another so have direct consequences on population abundances. Our model and it's implementation can estimate these interactions for many species, as well as include intraspecific interactions and facilitation. Our framework thus produces a better representation of the complexity of real plant communities and their interactions. This then allows us to do a bunch of cool stuff to a) better understand plant communities in general and b) better understand a specific plant system. Though our method still requires a lot of data, people interested in applications of this model (conservationists and ecosystem management) are likely to have access to the kind of monitoring data which is needed.  

    % Make it easier for empiricists to characterise species interactions in their system. Typically experimenters who want to build measure these things need to come up with complex models to resolve all interactions. If your data is plant annuals you can just plug your data right in. If it's a different type of species, you just need to adapt the population model and scaling of the interactions to work with your particular system. 

    % - deals with many species + measure of uncertainty
    % - deals with some unobserved interactions
    % - derived from pop dynamic models so direct consequences on pop abundances
    % - deals with facilitation 
    % - pairwise interactions (directional!)

    % -> better representation of complexity of real plant communities

    \subsection{Limitations}
        
        Though our framework does provide a way of estimating interactions between species which are not observed to cooccur, care should be taken that these unobserved interactions do not dominate a resulting network. The method we propose uses observed interactions to estimate simpler parameters which allow us to approximate the remaining interactions. This method thus works better the more observed interactions we have with which to estimate the unobserved ones. This method is not appropriate for datasets dominated by missing data on interactions.  It is also important to consider the likely reasons for missing interactions.  For instance, species pairs known to lack overlapping environmental requirements likely do not occur together do to environmental filtering that precedes interaction between individuals of the species.  It would not be appropriate to include such pairs in our framework. These interactions can be replaced with a 0... briefly bring up forbidden interactions, and how that framework (get a ref) could be helpful to people who have a lot of missing observations, or where there’s likely to be strong niche differences between species leading to no interactions. \\

        Our model framework is aimed to helping empiricists who want to estimate interactions for non-trophic horizontal communities - but these empiricists will still require large amounts of data. Though the MCMC sampling algorithm does allow for many parameters to be estimated, it is crucial to check chain-mixing and model behaviour to verify that the full parameter space is sampled. We wouldn't recommend fewer than 20 observations per focal species, and we do recommend grouping species which appear very very rarely (Give details, what criteria did I use? Can also say you can change that, especially if you know the system well...). More data will also give more precise estimates of interaction strengths.   


    \subsection{Applications to ecosystem management}

        Interaction networks provide a unique lens with which to examine an ecological community. Specifically, interaction networks allow us to determine important species which have particular effects on the wider community, as well as to examine how species of interest are affected by the whole community. These two aspects are particularly important to ecosystem management and conservation because they allow us to establish management strategies which are adapted to the community and species involved, and which acknowledge the interlinkedness of species and their effects on one another.  \\

        Certain species play important roles in the community which can be deduced from their position in the interaction network. Keystone species for example are both crucial to maintaining the organisation and diversity of their community, and have exceptionally strong effects on other species (Mills et al. 1993), often leading to secondary extinctions when they are removed from a network. In single-trophic systems, keystone species could be identified by their high in-strength ... Foundation species on the other hand ... Foundation species can be identified by high abundance, connectedness and predominantly facilitative interactions. \\

        Network approaches can also be used to determine how specific species are integrated within the community. We can determine whether invasive species are competing with or impacting many of the native species, or if they are disproportionally affecting a handful of species. Weak interactions between invasive and native species would indicate low resource sharing, such that the invasive species are probably exploiting 'empty' niche space rather taking over the niche space of natives. Threatened species would also benefit from this type of analysis, as we could deduce which other community members are hindering or helping their recovery. This is especially relevant for rare species, as recent work suggests they are the prime emitters and beneficiaries of facilitative interactions, forming mutualistic refuges from competitive dominants. If that is indeed the case, quantifying the interaction networks would help us identify which other species may be involved in 'propping up' the species of interest.  \\

        Overall, quantifying the community interaction network allows us to direct conservation and management efforts in ways which work with the community, rather than against it.

      
    \subsection{Understanding community diversity and stability}

        Quantifying the interaction networks of plant communities allows us to explore how the mechanisms maintaining diversity and stability operate across a broad number of species. Self-regulation, for example, is an extremely important driver of community stability (Barabas 2017 NEE) and arises from how individuals of the same species interact with one another. Whereas same-species effects cannot be estimated by association networks, our framework quantifies intraspecific interactions and allows us to measure the strength and prevalence of competitive and facilitative density-dependence. Measures of intra and interspecific interactions can also allow us to estimate niche overlap between species: weak interactions between species indicate they are not sharing or competing for many resources, and occupy different niche spaces in the community (ref??). Strong competitive self-regulation, and weak interactions between two species, are two of many mechanisms leading to continued coexistence in plant communities.\\

        A key feature of our model framework is the inclusion of facilitative interactions, which have long been disregarded in plant population models and theoretical frameworks of plant diversity-maintenance. The importance of facilitative interactions to community structure and patterns of abundance has long been recognised (Bruno Callaway 2003) but there is still little consensus on how they may affect coexistence between species. % MMM comment on ‘coexistence’: Needs to be clear if you have a good way to make this link or not – Maybe use ‘biodiversity’ or synonym, not coex? 
        Recent work suggests facilitation may be common (ref) and may harm or benefit species diversity and stability depending on the circumstances (ref). Our framework provides a means to investigate the prevalence and strength of facilitation across multiple species, and how it may act in relation to competition and species diversity.  \\
     
        Ultimately, quantifying plant interaction networks allows us to apply tools from network theory which will help us understand not only how plants interact, but also how these interactions drive community-level patterns of abundance and diversity. Several metrics already exist for describing network structure such as weighted connectance or relative intransitivity, though these are fewer than for trophic or bipartite networks. Adapting measures of nestedness or modularity for example to non-sparse networks (as plant communities typically are) would allow us to further characterise how interactions and species are organised. These metrics all relate to different aspects of stability and could greatly inform us on how diversity is maintained between plants.  

        Further avenues also exist to characterise how species tend to interact. Network motifs for example are the units which makes up a network, such as a three species food chain or an intransitive interaction loop. These motifs have important biological meaning. We could extend the network motif approach to single-trophic networks to characterise the kind of roles that species can occupy in relation to the wider plant community (Cirtwill ref!). \\



    \subsection{Future research directions}

    
    - adding trait or phylogeny data, for example by informing priors with trait or phylogeny distance matrix
    ie. improving our estimates \\
    - improving our knowledge of networks, developing tools for plant networks and tools that can deal with non-sparse networks, competitive and facilitative interactions \\
    - integrate with trophic networks (which appear to be sensitive to producer/plant network structure!)\\

    

\section{Supplementary Information}

    \subsection{STAN model code}

     

\end{document}